### 2020-11-06 book/bookdown-minimal-master/2_results.Rmd
Update 2_results.Rmd

standPlots<-cowplot::plot_grid(standVol.plot,standBA.plot,standK.plot,standQMD.plot,ncol=1,
                      align="v")

@@

# Summarize models
library(lmerTest)
anova(fit.vol, type="3") 
  rbind(anova(fit.ba, type="3"))
anova(fit.sph, type="3")

# Create estimated marginal means
ba.means <- emmeans(fit.ba, ~ BA.Target*Year)
sph.means <- emmeans(fit.sph, ~ BA.Target*Year)

# Contrasts
ba.contrast <- contrast(ba.means,interaction=c("pairwise","revpairwise")) 
sph.contrast <- contrast(sph.means,interaction=c("pairwise","revpairwise"))
```

@@

>>>>

standPlots<-cowplot::plot_grid(standVol.plot,standBA.plot,standK.plot,ncol=1,
                      align="v")

# could put in standQMD.plot as well

@@

# Summarize models
library(lmerTest)

# Create estimated marginal means
vol.means <- emmeans(fit.vol, ~ BA.Target*Year)
ba.means <- emmeans(fit.ba, ~ BA.Target*Year)
sph.means <- emmeans(fit.sph, ~ BA.Target*Year)

# Contrasts
vol.contrast <- contrast(vol.means,interaction="pairwise")
ba.contrast <- contrast(ba.means,interaction=c("pairwise")) 
sph.contrast <- contrast(sph.means,interaction=c("pairwise"))

# CREATE TABLES

# create the data frame of ANOVA
standFit.X<-
  data.frame(Variable="Volume",anova(fit.vol, type="3")) %>% 
  rbind(data.frame(Variable="Basal area",anova(fit.ba, type="3"))) %>% 
   rbind(data.frame(Variable="Stand density",anova(fit.sph, type="3"))) %>%

  # formatting
  rownames_to_column("Fixed effect") %>% 
  dplyr::select(Variable,`Fixed effect`,Sum.Sq:F.value,P.value="Pr..F.") %>% 
  mutate_at(vars("F.value","P.value"),round,5) %>% 
  mutate(`Fixed effect`=rep(c("Treatment","Year","Trt.*Year"),times=3)) %>% 
  rename(`Sum sq.`="Sum.Sq",
         `Mean sq.`="Mean.Sq",
         `Num. DF`="NumDF",
         `Den. DF`="DenDF",
         `F value`="F.value",
         `p value`="P.value")

# Create contrasts table
standFit.contrasts<-
  data.frame(Variable="Volume",vol.contrast) %>% 
  rbind(data.frame(Variable="Basal area",ba.contrast)) %>% 
  rbind(data.frame(Variable="Stand density",ba.contrast)) %>% 
  filter(Year_pairwise %in% c("1992 - 2019","1997 - 2019")) %>% 
  dplyr::select(Variable,`Year contrast`="Year_pairwise",`Treatment contrast`="BA.Target_pairwise",everything()) %>% 
  rename(`t ratio`="t.ratio",
         `p value`="p.value") %>% 
  mutate_at(vars(estimate:`t ratio`),round,3) %>% 
  mutate_at(vars(`p value`),round,5)

figNums("standFit.X",display=FALSE)

@@

`r tableNums("standFit.X",caption="Output from three separate linear models testing the effect of the interaction between treatment and year on plot-level volume, basal area and density." )`

```{r stand variable model output}

standFit.X %>% 
  flextable() %>% 
  align(align="left",part="all") %>% 
  merge_v(j="Variable") %>% 
  valign(valign="top",part="body") %>% 
    hline(i=c(3,6,9),border=fp_border(color="black")) %>% 
    fix_border_issues() %>% 
  autofit()
```
*Trt, treatment; Sq., squares, Num., numerator; Den., denominator; DF, degrees of freedom*

```{r show contrasts between plot means}
